---
title: "Computational Analysis"
author: "Huy Le"
output: 
  html_document:
    css: rany_style.css
    df_print: paged
    theme: default
    toc: yes
    toc_float:
      collapsed: true
    number_sections: true

knit: (function(inputFile, encoding) {
      out_dir <- '..';
      rmarkdown::render("ComputationalAnalysis.Rmd",
                        encoding=encoding,
                        output_file=file.path(dirname(inputFile), out_dir, 'ComputationalAnalysis.html')) })
---

<b> Definition: </b><br> - <b> Set: </b> Set of runs that include a predetermined number of in-scope regions. Each set will consider one more region compared to its preceding set.<br> - <b> Run: </b> A solving attempt with predetermined values for "Target Inequity Among Clusters" and "Target Inequity Within Cluster".<br> - <b> Time Limit: </b> Time limit for the solver is set at 1800 seconds.<br>

```{r setup, echo = F, include=FALSE}
options(scipen=999)
options(digits=2)
options(knitr.purl.inline = TRUE)

knitr::opts_knit$set(root.dir = normalizePath(".."))
```

```{r, echo = F, warning=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(writexl)
library(plotly)
library(DT)
library(highcharter)


```

```{r, echo = FALSE, warning=FALSE, message=FALSE}
displaytable <- function(data, rownames = FALSE, filter = 'none') {
  datatable(
    as.data.frame(data),
    rownames = rownames,
    extensions = list(Buttons = NULL),
    filter = filter,
    options = list(
      scrollY = TRUE,
      scrollX = TRUE,
      initComplete = JS("function(settings, json) {",
                        "$(this.api().table().header()).css({'background-color': '#013e77', 'color': '#fff'});",
                        "}"),
      dom = "Blfrtip",
      buttons = list(
        list(
          extend = "collection",
          buttons = c("csv", "excel", "pdf"),
          text = "Download"
        ),
        I("colvis")
      )
    )
  )
}
```

```{r, echo = F, warning=FALSE, message=FALSE}
# Load data
output <- read_excel("OptModel/Output/Revenue.xlsx") %>% 
  select(N_InScope, Threshold_Within, Threshold_Among, SolverTime, TerminationCondition, OptimalityGap) %>% 
  filter(as.numeric(N_InScope) <= 20) %>% 
  mutate(SolverTime = ifelse(SolverTime > 1800, 1800, SolverTime)) %>% 
  mutate(SolverTime = round(SolverTime,3),
         OptimalityGap = round(OptimalityGap,3))

setList <- unique(output$N_InScope)

output_clean <- output %>% mutate(N_InScope = factor(N_InScope, levels = setList)) %>% 
  arrange(N_InScope, Threshold_Within, Threshold_Among)
```

# Executive Summary
```{r, echo = F, warning=FALSE, message=FALSE}
n_set <- output_clean %>%
  summarise(`Number of Sets` = n_distinct(N_InScope))

n_run_per_set <- output_clean %>%
  summarise(`Number of Runs per Set` = n_distinct(Threshold_Within, Threshold_Among))

percentage_run_belowlimit <- output_clean %>% 
  group_by(N_InScope, TerminationCondition) %>% 
  summarise(`Number of Runs` = n()) %>% 
  ungroup() %>% 
  filter(TerminationCondition == "optimal") %>% 
  summarise(`Average Number of Below-Time-Limit Runs` = round(mean(`Number of Runs`),0))

time_per_set <- output_clean %>% group_by(N_InScope) %>% 
  summarise(TotalSolverTime = sum(SolverTime)) %>% 
  ungroup() %>% 
  summarise(`Average Solver Time per Set (seconds)` = round(mean(TotalSolverTime),0))

time_per_run <- output_clean %>% 
  filter(SolverTime < 1800) %>% 
  summarise(`Solver Time per Run - Excl Exceed-time-limit runs (seconds)` = round(mean(SolverTime),0))


kpis <- bind_cols(n_set, n_run_per_set, percentage_run_belowlimit, time_per_set, time_per_run) %>% 
  gather(key = "KPI", value = "Value")

kpis %>% displaytable()

```



```{r, echo = F, warning=FALSE, message=FALSE,out.width="100%"}

# n_runs_by_terminationcondition <- output_clean %>% 
#   group_by(N_InScope, TerminationCondition) %>% 
#   summarise(`Number of Runs` = n()) %>% 
#   ungroup()
#   
# 
# hchart(n_runs_by_terminationcondition, "column", hcaes(x =  "N_InScope", y = `Number of Runs`, group = "TerminationCondition")) %>%
#   hc_xAxis(title = list(text = "Number of In-scope Regions")) %>%
#   hc_yAxis(title = list(text = "Number of Runs"), max = 121) %>%
#   hc_title(text = "Number of Runs by Termination Condition and Number of In-scope Regions",
#            style = list(fontWeight = "bold",fontFamily = "Arial")) %>%
#   hc_chart(zoomType = "xy") %>%
#   hc_exporting(enabled = TRUE) %>% 
#   hc_colors(c("#00b4ae", "#013e77")) %>% 
#   hc_tooltip(crosshairs = TRUE, 
#     shared = TRUE, headerFormat = str_c("</b>{point.key}</b><br/>")) %>% 
#   hc_plotOptions(column = list(stacking = "normal"))

```

# Solver Time Analysis

## By Number of In-scope Regions
```{r, echo = F, warning=FALSE, message=FALSE,out.width="100%"}


solvertime_by_terminationcondition <- output_clean %>% 
  group_by(N_InScope, TerminationCondition) %>% 
  summarise(`Solver Time` = round(sum(SolverTime),0)) %>% 
  ungroup()
  
hchart(solvertime_by_terminationcondition, "area", hcaes(x = N_InScope, y = `Solver Time`, group = TerminationCondition), stacking = "normal") %>%
  hc_xAxis(title = list(text = "Number of In-scope Regions")) %>%
  hc_yAxis(title = list(text = "Solver Time (seconds)")) %>%
  hc_title(text = "Solver Time by Termination Condition and Number of In-scope Regions",
           style = list(fontWeight = "bold",fontFamily = "Arial")) %>%
  hc_chart(zoomType = "xy") %>%
  hc_exporting(enabled = TRUE) %>% 
  hc_colors(c("#00b4ae", "#013e77")) %>% 
  hc_tooltip(crosshairs = TRUE, 
             shared = TRUE, 
             headerFormat = "<b>Total Solver Time:</b> {point.total:,.0f} seconds<br/>",
              pointFormat = '<span style="color:{point.color}">\u25CF</span> <b>{series.name}:</b> {point.y:,.0f} ({point.percentage:,.3f} %) <br>')

dist <- ggplot(output_clean, aes(x = factor(N_InScope), y = SolverTime)) +
  geom_violin(color = "#013e77")+
  labs(title = "Solver Time per Run by Number of In-scope Regions (Excl Exceed-time-limit runs)",
       x = "Number of In-scope Regions",
       y = "Solver Time (seconds)") +
  ylim(0, 200)+
  theme(plot.title = element_text(face = "bold"))+
  theme_minimal()

dist%>% ggplotly() %>% 
  layout(font = list(family = "Arial")) %>% 
  layout(
    yaxis = list(
      tickvals = c(0, 25, 50, 75, 100, 125,150,175,200),  
      ticktext = c("0", "25", "50", "75", "100", "125", "150", "175", "200")
    )
  )

average_solvertime_perrun <- output_clean %>% 
  filter(TerminationCondition == "optimal") %>% 
  group_by(N_InScope) %>% 
  summarise(`Average Solver Time per Run` = mean(SolverTime))
  
hchart(average_solvertime_perrun, "column",
       hcaes(x = factor(N_InScope), y = `Average Solver Time per Run`)) %>%
  hc_title(text = "Average Solver Time per Run (Excl Exceed-time-limit runs)",
           style = list(fontWeight = "bold",fontFamily = "Arial")) %>%
  hc_xAxis(title = list(text = "Number of In-scope Regions")) %>%
  hc_yAxis(title = list(text = "Average Solver Time (seconds)")) %>%
  hc_colors(c("#013e77")) %>%
    hc_tooltip(crosshairs = TRUE,
    shared = TRUE, headerFormat = str_c("</b>{point.key}</b><br/>"),
    pointFormat = '<span style="color:{point.color}">\u25CF</span> <b>Average solver time:</b> {point.y:,.0f}  seconds<br>')
```

## By Target Inequity

```{r echo=F, message=FALSE, warning=FALSE, out.width="100%"}

solvertime_targetInequity <- output_clean %>% 
  group_by(Threshold_Among, Threshold_Within) %>% 
  summarise(`Average Solver Time` = round(mean(SolverTime),3)) %>% 
  ungroup() %>% 
  mutate(Threshold_Among = as.character(Threshold_Among),
         Threshold_Within = as.character(Threshold_Within))

adjusted_palette <- colorRampPalette(c("#00b4ae", "#013e77"))(100)



hchart(solvertime_targetInequity, "heatmap", 
       hcaes(x = Threshold_Among, y = Threshold_Within, value = `Average Solver Time`)) %>%
  hc_title(text = "Average Solver Time by Target Inequity",
           style = list(fontWeight = "bold",fontFamily = "Arial")) %>%
  hc_xAxis(title = list(text = "Target Inequity Among Clusters")) %>%
  hc_yAxis(title = list(text = "Target Inequity Within Cluster")) %>% 
  hc_colorAxis(stops = color_stops(n = 100, colors = adjusted_palette)) %>% 
  hc_legend(title = list(text = "Solver Time")) %>% 
  hc_tooltip(
    headerFormat = "",
    pointFormat = "Solver Time: {point.value}"
  )

hchart(solvertime_targetInequity, "heatmap", 
       hcaes(x = Threshold_Among, y = Threshold_Within, value = round(log(`Average Solver Time`),3))) %>%
  hc_title(text = "Average Solver Time by Target Inequity",
           style = list(fontWeight = "bold",fontFamily = "Arial")) %>%
  hc_xAxis(title = list(text = "Target Inequity Among Clusters")) %>%
  hc_yAxis(title = list(text = "Target Inequity Within Cluster")) %>% 
  hc_colorAxis(stops = color_stops(n = 100, colors = adjusted_palette)) %>% 
  hc_legend(title = list(text = "ln(Solver Time)")) %>% 
  hc_tooltip(
    headerFormat = "",
    pointFormat = "ln(Solver Time): {point.value}"
  )


```

# Optimality Gap Analysis

```{r echo=F, message=FALSE, warning=FALSE, out.width="100%"}

optimality_targetInequity <- output_clean %>% 
  group_by(Threshold_Among, Threshold_Within) %>% 
  summarise(`Average Optimality Gap` = round(mean(OptimalityGap))) %>% 
  ungroup() %>% 
  mutate(Threshold_Among = as.character(Threshold_Among),
         Threshold_Within = as.character(Threshold_Within))

adjusted_palette <- colorRampPalette(c("#00b4ae", "#013e77"))(100)

hchart(optimality_targetInequity, "heatmap", 
       hcaes(x = Threshold_Among, y = Threshold_Within, value = `Average Optimality Gap`)) %>%
  hc_title(text = "Average Optimality Gap by Target Inequity",
           style = list(fontWeight = "bold",fontFamily = "Arial")) %>%
  hc_xAxis(title = list(text = "Target Inequity Among Clusters")) %>%
  hc_yAxis(title = list(text = "Target Inequity Within Cluster")) %>% 
  hc_colorAxis(stops = color_stops(n = 100, colors = adjusted_palette)) %>% 
  hc_legend(title = list(text = "Optimality Gap")) %>% 
  hc_tooltip(
    headerFormat = "",
    pointFormat = "Average Optimality Gap: {point.value}"
  )


```

# Appendix

```{r echo=F, message=FALSE, warning=FALSE, out.width="100%"}
output_clean %>% 
  rename(`Number of In-scope Regions` = N_InScope,
         `Target Inequity Within Cluster` = Threshold_Within,
         `Target Inequity Among Cluster` = Threshold_Among) %>% 
  displaytable()


```
